Measles risk assessment and cost interim report\\ \vspace{2 mm} {\large David T S Hayman, Tim Carpenter,\\ Jonathan C Marshall, Mick Roberts, Nigel P French}

### 2014-07-02 interimreport1.tex
R0 figures included
Included R0 estimation and figures in the report text.

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<echo=FALSE>>=
library(xtable)
dpdf<-read.csv("mapdata.csv",header=T)
# output top countries
topimmigration <- dpdf[order(-dpdf$immigration),] 
immigration<-topimmigration[1:10,c(1,4)]
topincidence <- dpdf[order(-dpdf$incidence),] 
incidence<-topincidence[1:10,c(1,2)]
incidence[,2]<-round(incidence[,2],0)
topvaccine <- dpdf[order(dpdf$cover),] 
vaccinecover<-topvaccine[1:10,c(1,3)]
toprisk <- dpdf[order(-dpdf$risk),] 
risk<-(toprisk[1:10,c(1,5)])
risk[,2]<-round(risk[,2],0)
@

\begin{table}
\caption{Immigration to New Zealand (2012)}
<<results=tex,echo=FALSE>>=
# This chunk uses "results=tex"
library(Hmisc)
latex(immigration, file="", table.env=FALSE,rowname=NULL)
@
\end{table}

\begin{table}
\caption{Lowest national measles vaccine cover (2012)}
<<results=tex,echo=FALSE>>=
# This chunk uses "results=tex"
library(Hmisc)
latex(vaccinecover, file="", table.env=FALSE,rowname=NULL)
@
\end{table}

\begin{table}
\caption{Measles Incidence per million (2012)}
<<results=tex,echo=FALSE>>=
# This chunk uses "results=tex"
library(Hmisc)
latex(incidence, file="", table.env=FALSE,rowname=NULL)
@
\end{table}

\begin{table}
\caption{Risk of measles importation to New Zealand in 2012}
<<results=tex,echo=FALSE>>=
# This chunk uses "results=tex"
library(Hmisc)
latex(risk, file="", table.env=FALSE,rowname=NULL)
@
\end{table}

@@

<<echo=FALSE>>=
# haven't had time to sort out which packages I need
library(maps)       # Provides functions that let us plot the maps
library(mapdata)    # Contains the hi-resolution points that mark out the countries.
library(rworldmap)
library(adehabitat)
library(rgdal)
library(raster)
library(maps)
library(maptools)
library(sp)
#library(SDMTools)
library(ggplot2)
require(rgeos)
library(ggmap)
library(mapdata)
#gpclibPermit()
library(mapproj)
library(plyr)
library(grid)
library(gridExtra)
#gpclibPermit()
library(utils)
library(rgdal)
#getwd()
#setwd("~/data")
#unzip("TM_WORLD_BORDERS_SIMPL-0.3.zip")
load("world.ggmap.Rda")
n <- length(unique(world.ggmap$id))
id = unique(world.ggmap$id)
id<-as.data.frame(id)
dpdf<-read.csv("mapdata.csv",header=T)
# output top countries

np1<-ggplot(dpdf, aes(map_id = id)) +ggtitle("Immigration") +
  geom_map(aes(fill = immigration), map =world.ggmap) +
  expand_limits(x = world.ggmap$long, y = world.ggmap$lat) +
   xlab("longitude") +
  ylab("latitude") +
  scale_fill_gradient("",low = "blue", high = "red", guide = "colorbar")

np2<-ggplot(dpdf, aes(map_id = id)) +ggtitle("Incidence (per million)") +
  geom_map(aes(fill = incidence), map =world.ggmap) +
  expand_limits(x = world.ggmap$long, y = world.ggmap$lat) +
  xlab("longitude") +
  ylab("latitude") +
  scale_fill_gradient("",low = "blue", high = "red", guide = "colorbar")

np3<-ggplot(dpdf, aes(map_id = id)) +ggtitle("Vaccination cover (%)") +
  geom_map(aes(fill = cover), map =world.ggmap) +
  expand_limits(x = world.ggmap$long, y = world.ggmap$lat) +
  xlab("longitude") +
  ylab("latitude") +
  scale_fill_gradient("",low = "red", high = "blue", guide = "colorbar")

#grid.arrange(np1, np2, np3, ncol=3, main="")

np4<-ggplot(dpdf, aes(map_id = id)) +
  geom_map(aes(fill = risk), map =world.ggmap) +
  expand_limits(x = world.ggmap$long, y = world.ggmap$lat) +
   xlab("longitude") +
  ylab("latitude") +
  theme(text = element_text(size=30))+
  scale_fill_gradient("",low = "yellow", high = "red", guide = "colorbar")
#np4
@

\begin{figure}[h!]
\caption{Global risk data 2012: Immigration numbers to New Zealand (top); Measles incidence (per million) (middle); Vaccination coverage (bottom)}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 5>>=
print(grid.arrange(np1, np2, np3, ncol=1, main="2012"))
@
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
<<fig=TRUE,echo=FALSE,width = 11>>=
print(np4)
@
\end{center}
\caption{Risk map from measles incidence and immigration rates}
\end{figure}

@@

\begin{figure}[p]
     \centering
     \includegraphics[width=0.8\textwidth]{averageR0.pdf}
     \caption{Test image}
     \label{fig:test image}
\end{figure}

>>>>

\usepackage{Sweave}
\begin{document}
\input{interimreport1-concordance}

@@

\begin{table}
\caption{Immigration to New Zealand (2012)}
%latex.default(immigration, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lr}
\hline\hline
\multicolumn{1}{c}{id}&\multicolumn{1}{c}{immigration}\tabularnewline
\hline
Australia&$809775$\tabularnewline
United Kingdom&$306177$\tabularnewline
China&$256036$\tabularnewline
United States&$194438$\tabularnewline
Japan&$ 86676$\tabularnewline
Germany&$ 83608$\tabularnewline
Korea, Republic of&$ 73459$\tabularnewline
France&$ 71448$\tabularnewline
India&$ 69038$\tabularnewline
Canada&$ 54981$\tabularnewline
\hline
\end{tabular}\end{center}\end{table}

\begin{table}
\caption{Lowest national measles vaccine cover (2012)}
%latex.default(vaccinecover, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lr}
\hline\hline
\multicolumn{1}{c}{id}&\multicolumn{1}{c}{cover}\tabularnewline
\hline
Equatorial Guinea&$34$\tabularnewline
Somalia&$49$\tabularnewline
Lesotho&$60$\tabularnewline
Central African Republic&$65$\tabularnewline
Papua New Guinea&$67$\tabularnewline
Chad&$69$\tabularnewline
Haiti&$69$\tabularnewline
South Sudan&$70$\tabularnewline
Gabon&$71$\tabularnewline
Yemen&$71$\tabularnewline
\hline
\end{tabular}\end{center}\end{table}

\begin{table}
\caption{Measles Incidence per million (2012)}
%latex.default(incidence, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lr}
\hline\hline
\multicolumn{1}{c}{id}&\multicolumn{1}{c}{incidence}\tabularnewline
\hline
Equatorial Guinea&$1617$\tabularnewline
Nauru&$1100$\tabularnewline
Democratic Republic of the Congo&$1096$\tabularnewline
Somalia&$ 979$\tabularnewline
Djibouti&$ 824$\tabularnewline
Sudan&$ 786$\tabularnewline
Burkina Faso&$ 447$\tabularnewline
Romania&$ 342$\tabularnewline
Ukraine&$ 280$\tabularnewline
Sudan&$ 229$\tabularnewline
\hline
\end{tabular}\end{center}\end{table}

\begin{table}
\caption{Risk of measles importation to New Zealand in 2012}
%latex.default(risk, file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{lr}
\hline\hline
\multicolumn{1}{c}{id}&\multicolumn{1}{c}{risk}\tabularnewline
\hline
United Kingdom&$10202161$\tabularnewline
Australia&$ 6991116$\tabularnewline
Malaysia&$ 3226580$\tabularnewline
Thailand&$ 1576414$\tabularnewline
China&$ 1138900$\tabularnewline
India&$ 1039356$\tabularnewline
Indonesia&$  984022$\tabularnewline
Ukraine&$  664315$\tabularnewline
Ireland&$  585413$\tabularnewline
Romania&$  490731$\tabularnewline
\hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics{interimreport1-007}
\end{center}
\caption{Immigration to New Zealand 2012}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics{interimreport1-008}
\end{center}
\caption{Measles incidence per million 2012}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics{interimreport1-009}
\end{center}
\caption{Measles vaccination cover (\%) 2012 }
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics{interimreport1-010}
\end{center}
\caption{Risk map from measles incidence and immigration rates}
\end{figure}

@@

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{incidence_1997_2014.pdf}
     \caption{Measles incidence from 1997 to 2014}
     %\label{fig:test image}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{cases_by_dhb_2009_2014.pdf}
     \caption{Measles cases by DHB from 2009 to 2014}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{outbreaks_for_R0.pdf}
     \caption{Measles data classified as outbreaks for R0 estimation}
     \label{fig:outbreaks}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.8\textwidth]{averageR0.pdf}
     \caption{Estimates of R0 for the outbreaks each year, as classified in Figure~\ref{fig:outbreaks} (page~\pageref{fig:outbreaks})}
\end{figure}
